Age-related changes in plant growth and traits

### 2015-09-08 leaf_weight_issue.Rmd
fixed typo with color scheme

plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)

plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)

>>>>

plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data2[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)

plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data1[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)
